Optimize the Cannon 2

### 2016-10-26 paper/ms.tex
Add delta-chi-squared

@@

 Choose four stellar, which are not in the training set. Optimize the spectrum of these four stars and obtain a, b and c.

 The result is \(a+b+c = 0.999\).

(a,b,c) = (0.078, 0.886, 0.035).

The values of the objective function before and after are 177254 and 174031
, which decreases by 2\%.

@@

@@

%\includegraphics[width=170mm]{figure_3.png}

@@

This figure gives us information about the relation between parameters a, b, c and fiber number, which can be used to establish a data-driven spectrum calibration model.

>>>>

In our experiment except calculating $\theta_{j}$, we calculate a, b and c independently for each star, which means N=1 in formula(4)(5)(6)(7).

@@

 Choose four stellar, which are not in the training set. Optimize the spectrum of these four stars and obtain a, b and c for each stars.

@@

\begin{table}[ht]
\caption{Fitting results for the four stars}
\centering
\begin{tabular}{c c c c c}
\hline\hline
Star Name & a & b & c & a+b+c \\ [0.5ex] % inserts table %heading
\hline
Star A & 0.121 & 0.824 & 0.052 & 0.998 \\
Star B & 0.176 & 0.541 &  0.278 & 0.995 \\
Star C & 0.003 & 1.004 &  -0.007 & 1.000 \\
Star D & -0.009  & 1.029 & -0.020 & 1.000 \\ [1ex]
\hline
\end{tabular}
\label{table:nonlin}
\end{table}

@@

%\includegraphics[width=170mm]{figure_3.png}
\bigskip

\centerline{Fig.3 Histogram for  a, b and c}

@@

\centerline{Fig.4 a,b,c vs Mean Fiber Number}
\bigskip

This figure gives us information about the relation between parameters a, b, c and fiber number, which can be used to establish a data-driven spectrum calibration model.
\bigskip

We also plot delta-chi-squared vs Mean Fiber number, where delta-chi-squared is the difference between the chi-squared of the spectrum before our optimization and after. It should be bigger than 0.
\bigskip

%\includegraphics[width=170mm]{figure_5.png}
\bigskip

\centerline{Fig.5 Delta-chi-squared vs Mean Fiber Number}
\bigskip
